Trinity: A Language for Multi-View Architecture Description and Control\titlenote{with optional title note}

### 2017-07-27 sigplanconf-template.tex
more of Early Design + title

\title{Title Text\titlenote{with optional title note}}
\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

@@

>>>>

\title{Trinity: A Language for Multi-View Architecture Description and Control\titlenote{with optional title note}}
\subtitle{Subtitle Text, if any\titlenote{with optional subtitle note}}

@@

	Trinity is designed to safeguard communication integrity, which is a top priority in regards to desired guarantees to preserve in end-product implementations. To enforce communication integrity is to ensure that “each component in [an] implementation may [communicate] directly with … components to which it is connected in the architecture.” In our early implementation of Trinity, we have provided support for a “hard-coded” Component-and-Connector view of a Wyvern software system. Our design translates concepts from software architecture into implementation capabilities.

	Entities in the Cnc architecture view are keywords/types/objects in Trinity. An entire software architecture, comprised of components and connectors, is contained within an architecture object/type/keyword. Trinity components are runtime components such as servers, clients, and databases. Ports are fields of a component that act as access points to interact with other components; these include interfaces that provide details about the interface another component must fulfill to communicate with said component through said port. Connectors, such as JDBC connectors, connect multiple ports of components. Attachments allow the programmer to “actually” connect components using ports of components and provided connectors. An entryPoint is an access point for a program using the specified architecture. It might be a function of a particular component in the architecture. For example, an architecture describing a three-tier web application might have an entryPoint specified by the “start()” function of a client component. Bindings allow the programmer to alias functions of components, to reduce code verbosity.
